\chapter*{Goal, Objectives and Project Plan}
\addcontentsline{toc}{chapter}{Goal, Objectives and Project Plan}

In this Final Year Project (FYP), the goal is to develop an advanced DL-based method for SSL and explore the possibilities of deploying the DNN on a mobile platform for real-time SSL.

The objectives of this project are to:
\begin{enumerate}
    \item Investigate the mathematical-model-based traditional SSL approaches by reproducing the experiment of SSL using these algorithms, establishing standards for the development of DNN.
    \item Conduct research on the performance of the state-of-the-art DNNs' architectures, reproducing the DoA estimation process of these DNNs by using the computationally generated dataset.
    \item Develop an accurate DNN structure to predict the location of a stationary sound source and further develop a DNN structure for real-time sound source trajectory tracking.
    \item Develop a mobile platform based on the Robot Operating System (ROS) and develop the software program for the deployment of newly developed SSL approaches, enabling the platform to react to the sound source.
    \item Conduct field tests using the real-world audio data to evaluate the performance of the DL approaches and conduct experiments to evaluate the mobile platform's performance regarding a sound source.
\end{enumerate}

These objectives are categorized into three parts: the traditional SSL algorithm, the DL-based SSL algorithm, and the mobile platform. These parts are assigned to XIAO Pengbo, ZENG Bailin, and WU Zhuoli, respectively. The detailed schedule of this FYP is described in \textit{the Gantt Chart for Task Schedule} section of the appendices.



